
\section{Experience}

\outerlist{

\entrybig
	{\textbf{Alberta Machine Intelligence Institute}}{Edmonton, AB, Canada}
	{Training Program}{2021\textendash 2022}
\innerlist{
	\entry{Assisted in consulting with industry partners to help with the
			integration of ML for solutions in their current workflow.}
}

\entrybig
	{\textbf{University of Alberta}}{Edmonton, AB, Canada}
	{Computing Science Teachers Assistant}{2021\textendash 2022}
\innerlist{
	\entry{Created solutions to programming lab assignments in C.}
	\entry{Wrote automation scripts for verifying the compilation and marking
            of students assignments using Python and Bash.}
	\entry{Held office hours to assist students with questions about algorithms,
            C syntax and semantics, and code implementation.}
}

\entrybig
	{\textbf{Agriculture \& Agri-Food Canada}}{Brandon, MB, Canada}
	{Research Assistant}{2017\textendash 2021}
\innerlist{
	\entry{Developed a Python and PyTorch tool that implemented a convolutional 
            neural network algorithm to perform phenotype prediction of fusarium 
            head blight (FHB) infection and deoxynivalenol (DON) levels in 
            barley using genome data as part of a barley pathology program. }
	\entry{Collaborated with a Bioinformatics PhD candidate to build regression 
            models with multiple data encodings. Involved transforming 
            sequencing data between encodings using Python tools, and building 
            the models in JMP Genomics.}
	\entry{Performed statistical analysis, data preprocessing, and data 
            visualization using JMP Genomics/SAS and Python modules to support 
            the research of the barley breeding program. }
	\entry{Communicated clearly to varying levels of authority and across 
            multiple levels of scientific understanding. }
}

\entrybig
	{\textbf{Brandon University}}{Brandon, MB, Canada}
	{Computer Science Lab Assistant}{2018\textendash 2021}
\innerlist{
	\entry{Mentored and assisted students in the completion of Java programming 
            exercises by helping them understand the fundamentals of 
            object-oriented programming and arrive at their own conclusions.}
	\entry{Aided students in debugging their programs, clearly explain Java 
            error codes, and help them understand the importance of program 
            design, testing, and proper implementation techniques.}
}

% \entrybig
% 	{\textbf{Canada Manitoba Crop Diversification Centre}}{Carberry, MB, Canada}
% 	{Student Research Assistant}{Summer 2014, 2015, 2016}
\newline
}

